Evaluating `Graphical Perception' with CNNs

### 2018-03-30 PAPER/04_position_angle_experiment.tex
Update 4.

	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{figure3_Bar_Chart.pdf}} & \makecell[tl]{Type 1: \emph{Bar Chart}\\~~~Perceptual Task: \emph{Position}\\~ \\~ \\} &~& \makecell[tr]{~\\ $244,827$}\\

	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{figure3_Pie_Chart.pdf}} & \makecell[tl]{Type 2: \emph{Pie Chart}\\~~~Perceptual Task: \emph{Angle}\\~ \\~ \\} &~& \makecell[tr]{~\\ $244,827$}\\

>>>>

	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{figure3_Bar_Chart.pdf}} & \makecell[tl]{Type 1: \emph{Bar Chart}\\~~~Perceptual Task: \emph{Position}\\~ \\~ \\} &~& \makecell[tr]{~\\ $878,520$}\\

	\midrule
	\raisebox{-.85\height}{\includegraphics[width=.5in]{figure3_Pie_Chart.pdf}} & \makecell[tl]{Type 2: \emph{Pie Chart}\\~~~Perceptual Task: \emph{Angle}\\~ \\~ \\} &~& \makecell[tr]{~\\ $878,520$}\\
